\documentclass[10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{tabularx}
\usepackage{float}
\usepackage{babel}[polish]

\usepackage[margin=1in]{geometry}

\usepackage{hyperref}

\author{Igor Motyka}
\title{Resume}

 \renewcommand{\maketitle}{
 \begin{center}
    \huge\bfseries\theauthor
 \end{center}
 \begin{center}
    \href{mailto:igor\_motyka@mail.com}{igor\_motyka@mail.com}\\
 \end{center}
 \begin{center}
	 \href{https://github.com/Anav0}{Github} \hspace{0.7cm} \href{https://www.linkedin.com/in/igor-m-873439168/}{Linkedin} \hspace{0.7cm} \href{https://igormotyka.netlify.app/}{My website}
 \end{center}
 }
\renewcommand{\familydefault}{\rmdefault}
\DeclareTextFontCommand{\emph}{\bfseries\em}

\titleformat{\section}
{\huge\bfseries}{}{0em}{}[\titlerule]

\titleformat{\subsection}
{\Large\bfseries}{}{0em}{}

\titleformat{\subsubsection}
{\large\bfseries}{$\bullet$}{1em}{}

\renewcommand{\arraystretch}{0}

\begin{document}

\maketitle

\section{Education}
\subsection{University of Opole}
\subsubsection{Masters of Computer Science 2020 - 2021}
\begin{table}[H]
    \begin{tabularx}{\textwidth}{@{}l X}
     \textbf{Dissertation thesis:} & \textit{``Design and implementation of a simulated annealing algorithm for scheduling rehabilitation appointments``} \\
    \end{tabularx}
\end{table}
\noindent In this thesis I've tried to solve rehabilitation scheduling problem. For that I have developed universal framework that allowed user to describe his optimization problem and then to hopefully produce good enough solutions. Framework was written in \emph{.Net 5.0} but efficiency analysis was partly written in \emph{jupyter notebook}.
\\\\
I did not attend my thesis defence (it's a long story, trust me)
\subsubsection{Bachelor of Computer Science 2016 - 2020}
\begin{table}[H]
    \begin{tabularx}{\textwidth}{@{}l X}
    \textbf{Dissertation thesis:} &  \textit{``Example of instant messenger featuring chatbot implementation``}\\
    \end{tabularx}
\end{table}
\noindent As my engineering project I've created \href{https://www.behance.net/gallery/91600605/Gymba-chat}{\underline{chat application}} with \emph{Vue}, \emph{Node js}, \emph{socket.io} and \emph{MongoDb}.
\section{Career}
\subsection{Capgemini: Feb 2022 (present)}
Working with Credit Suisse on further development of their risk assessing software.
\subsection{PKO Bank Polski: Nov 2021 - Feb 2022 (3 months)}
At PKO I was tasked with further development of software responsible for creating credit offer for individual customers.
\\\\
\textbf{Reasons for resignation:} My salary was 30\% lower than it should be. Project manager lied to me about brand new innovative project that I would take part in the near future. In reality there was no project in sight.
\newpage
\subsection{Medinet: Jun 2020 - Nov 2021 (1.5 year)}
At Medinet I was working on optimizing process of scheduling rehabilitation appointments. For that purpose I've taken care of frontend, backend, deployment and CI processes.
\\\\
It was an informal cooperation as part of my masters thesis.
\subsection{BCF Software Jul 2019 - Dec 2019 (5 months) }
At BCF Softwere I was working as frontend developer with React, Vue and Nuxt. Some project that I helped create are:
    \href{https://cryptogamble.com}{cryptogamble.com}, \href{https://lotterija.com}{lotterija.com}, \href{https://bgs.bet}{bgs.bet}.
\\\\
\textbf{Reasons for resignation:} 
I was studying, writing my thesis and working at the same time and it was too much for me. Just commuting one way to work took an hour and a half.
\section{Skills}
\subsection{Programming}
\renewcommand{\arraystretch}{2.5}
\begin{table}[H]
    \begin{tabularx}{\textwidth}{@{}l X}
         \textbf{Rust} & My favourite language of them all. Up to this point I've written: \href{https://github.com/Anav0/papcio-rs}{\underline{epub reader}}, \href{https://github.com/Anav0/png-rs}{\underline{png file parser and secret messages encoder}}, \href{https://github.com/Anav0/hex-rs}{\underline{hex editor}}, \href{https://github.com/Anav0/genetic-draw-rs}{\underline{genetic image drawer}}, \href{https://github.com/Anav0/ubuntu-bootstrap-rs}{\underline{linux system bootstraper}}\\
         \textbf{C\#} & I can write code that executes in parallel, I know how to use memoization. Dictionary and StringBuilder are my friends. I know most of design patterns from book: \emph{``Head first: design patterns``}.\\
         \textbf{.Net} & I can write standalone NuGet packages, REST API with SQL or Mongo backend. I remember some WPF if need be. I know fundamental principals of microservices architecture. \\
         \textbf{Ms SQL, Postgres, MySql} & I can write queries without creating index for every column and making too many joins. \\
         \textbf{MongoDb} & I've used it in my engineering project along with \emph{Mongoose ORM}. \\
	 \textbf{Javascript / Typescript} & I know about ES6, event loop and prototypes.\\
	 \textbf{Node.js} & I can create standard backend with REST API.\\
         \textbf{Frontend frameworks} & I know good chunk of them in different level of proficiency. Here they are listed from best known to least: \bfseries \em Svelte, React, Gatsby, Nuxt, Vue. \\
         \textbf{Gsap} & I can animate complex svg files.\\
	 \textbf{C} & I know the basics.\\
         \textbf{Python} & I'm able to write Flask API, python scripts e.g scraping websites or implementing some CS algorithm (Moore, Hoopcroft). Apart from that I'm competent enough to analyse data and produce nice plots (\bfseries \em matplotlib, pandas, seaborn, numpy). \\

    \end{tabularx}
\end{table}
\subsection{Misc}
\begin{table}[H]
        \begin{tabularx}{\textwidth}{@{}l X}
         \LaTeX & I can write palatable documents. \\
          \textbf{Google Cloud Platform (GCP)} & I can build docker images via pipline and publish them on GCP Cloud Run. I can use buckets.  \\
           \textbf{Github actions} & I can create pipelines to build, test and publish.  \\
\end{tabularx}
\end{table}
\section{Languages}
\begin{table}[H]
        \begin{tabularx}{\textwidth}{@{}l X}
         \bfseries English & C1. \\
         \bfseries Polish & Native.  \\
\end{tabularx}
\end{table}
\section{Certificates}
\Large \textbf{Software Development Fundamentals} (Jun 2019) \vspace{0.3em}\\
\large Microsoft \vspace{0.5em} \\
\small ID dPYP-DTRs \\
\section{Interests}
\begin{itemize}
    \item \href{http://cejsh.icm.edu.pl/cejsh/element/bwmeta1.element.desklight-b5b6fec4-8161-42ac-9a31-c0e6c344f9fa}{Sunni and shia propaganda in poetry}.
    \item Historical wargaming.
    \item Strolling across communist era districts in my city to admire architecture.
\end{itemize}
\vfill
\begin{center}
I allow anyone who is in possession of this document to use it for any necessary recruitment processes.
\end{center}
\end{document}

